Figure 1-Supplement 1b

### 2018-02-14 inst/tcga_expression/tcga_expression.Rmd
name change for tcga_expression

---
title: "Figure 1-Supplement 1b"
subtitle: "miR34a asRNA and miR34a TCGA expression"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

##prepare for plotting
data <- data %>%
  mutate(TP53 = if_else(TP53 == 0, "TP53 wt", "TP53 mut")) %>%
  select(TCGA_cancer_id, TP53, cancer_PAM50, RP3, miR34a) %>%
  gather(gene, value, -(TCGA_cancer_id:cancer_PAM50)) %>%
  mutate(gene = if_else(gene == "RP3", "miR34a asRNA", "miR34a"))

@@

#add fake data where p53 mut is missing (will be hidden in plot) to keep empty space
data <- data %>%
  mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
  mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))

stats <- stats %>%
  mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
  mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))
```

>>>>

---
title: "Figure 1-Supplement 1b"
subtitle: "miR34a asRNA and miR34a TCGA expression"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

##prepare for plotting
data <- data %>%
  mutate(TP53 = if_else(TP53 == 0, "TP53 wt", "TP53 mut")) %>%
  select(TCGA_cancer_id, TP53, cancer_PAM50, RP3, miR34a) %>%
  gather(gene, value, -(TCGA_cancer_id:cancer_PAM50)) %>%
  mutate(gene = if_else(gene == "RP3", "lncTAM34a", "miR34a"))

@@

#add fake data where p53 mut is missing (will be hidden in plot) to keep empty space
data <- data %>%
  mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
  mutate(gene = parse_factor(gene, levels = c("lncTAM34a", "miR34a"))) %>%
  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))

stats <- stats %>%
  mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
  mutate(gene = parse_factor(gene, levels = c("lncTAM34a", "miR34a"))) %>%
  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))
```
